### 2018-12-15 Src/paper.tex
work started on document

\documentclass[11pt]{article}
\usepackage{epsfig}
\usepackage{cite}
\usepackage{amssymb}
\usepackage{amsmath}
\setlength\topmargin{1.5pc} \setlength\textheight{600pt}
\setlength\textwidth{32pc}

\newcommand{\dbtable}[5]{{\small\begin{tabular}[t]{#2}
      \hline
      \multicolumn{#1}{|l|}{#3} \\
      \hline \hline
      #4 \\
      \hline
      #5 \\
      \hline
\end{tabular}}}
\title{Verified Time Balancing of Security Protocols 
  \\ \large A Case Study}

\author{Student Name: Donovan Crichton\\
Student Number: u6881864}
\date{}

\begin{document}

\maketitle

\section*{A description of the ZRTP Protocol}
  \subsection*{Syntax}
  \subsubsection{$p$}
  $p$ represents the message preamble $0x505a$ followed
  by a 16-bit length in 32-bit words, followed by the message
  type 2-word block string (e.g.) ``hello''.
  \subsubsection{$v$}
  $v$ represents the 4-character long string containing the
  version of the ZRTP protocol.
  \subsubsection{$cid$}
  $cid$ represents the client identificationn string which
  identifies the vendor and release of the ZRTP software.
  \subsubsection($h3$)
  $h3$ represents the following: \\
    $h0$ representing a 256-bit random nonce. \\
    $h1$ representing a hash of $h0$ with SHA-256.\\
    $h2$ representing a hash of $h1$ with SHA-256.\\
    $h3$ representing a hash of $h2$ with SHA-256.
  \subsubsection($zid$)
  test
  \subsection{Messages}
  \subsubsection{Hello}
  Alice says hello to Bob.
  \begin{align*}
          alice_0(p, v, cid, h3, zid, flags, hashAlgs, 
            cipherAlgs, authTags, keyAgreements, SAStypes, mac)
  \end{align*}

\end{document}

### 2018-12-15 Src/paper.tex
Some work on formal documentation

@@
 \maketitle
-
-\section*{A description of the ZRTP Protocol}
-  \subsection*{Syntax}
-  \subsubsection{$p$}
-  $p$ represents the message preamble $0x505a$ followed
-  by a 16-bit length in 32-bit words, followed by the message
-  type 2-word block string (e.g.) ``hello''.
-  \subsubsection{$v$}
-  $v$ represents the 4-character long string containing the
-  version of the ZRTP protocol.
-  \subsubsection{$cid$}
-  $cid$ represents the client identificationn string which
+  \section*{The Message Preamble}
+  All ZRTP Messages are prefixed by a preamble, message length
+  and message type. 
+  \begin{itemize}
+  \item Let $p$ represent the message preamble $0x505a$ followed
+        by a 16-bit length in 32-bit words, followed by the 
+        message type 2-word block string (e.g. ``hello'').
+  \end{itemize}
+  \section*{The Hello Messages}
+  \begin{itemize}
+    \item Let $p$ represent the message preamble.
+    \item Let $v$ represent the 4-character long string containing 
+          the version of the ZRTP protocol.
+    \item Let $c$ represent the client identification string which
           identifies the vendor and release of the ZRTP software.
-  \subsubsection($h3$)
-  $h3$ represents the following: \\
-    $h0$ representing a 256-bit random nonce. \\
-    $h1$ representing a hash of $h0$ with SHA-256.\\
-    $h2$ representing a hash of $h1$ with SHA-256.\\
-    $h3$ representing a hash of $h2$ with SHA-256.
-  \subsubsection($zid$)
+    \item Let $h3$ represent the following:
+       \begin{itemize}
+       \item Let $h0$ represent a 256-bit random nonce.
+       \item Let $h1$ represent a hash of $h0$ with SHA-256.
+       \item Let $h2$ represent a hash of $h1$ with SHA-256.
+       \item Let $h3$ represent a hash of $h2$ with SHA-256.
+       \end{itemize}
+    \item Let $z$ represent the 96-bit long unique identifier for 
+          the ZRTP endpoint. This is a random number generated at 
+          installation time to act as a key when looking up 
+          shared secrets in a local cache.
+    \item Let $fs$ represent a 4-bit long sequence of flags. 
+          The leading bit is 0, the second represents a 
+          signature-capable flag, the third a MiTM flag to 
+          identify that this message was sent from a PBX. The 
+          fourth and final bit represents a passive flag 
+          whichis only used on devices that send hello, 
+          but will never send commit messages.
+    \item Let $hc$ represent the number (count) of hashing 
+            algorithms.
+    \item Let $cc$ represent the number of cipher algorithms.
+    \item Let $ac$ represent the number of auth tag types.
+    \item Let $kc$ reresent the number of key agreement types.
+    \item Let $sc$ represent the number of SAS types.
+    \item Let $hs$ represent the ordered set of hashing algorithms.
+    \item Let $cs$ represent the set of cipher algorithms.
+    \item Let $as$ represent the set of SRTP auth tag types.
+    \item Let $ks$ represent the set of key agreement types.
+    \item Let $ss$ represents the set of short authentication 
+          string types.
+    \item Let $m$ represents the machine authentication code 
+          that finishes the ZRTP message.
+  \end{itemize}
+  \subsection*{Alice says Hello to Bob.}
+   $alice_0(p,v,c,h3,z,fs,hc,cc,ac,kc,sc,hs,cs,as,ks,ss,m)$
+  \subsection*{Bob receives Alice's Hello.}
+   $bob_0(p_{a0},v_{a0},c_{a0},h3_{a0},z_{a0},fs_{a0},hc_{a0}
+     ,cc_{a0},ac_{a0},kc_{a0},sc_{a0},hs_{a0},cs_{a0}
+          ,as_{a0},ks_{a0},ss_{a0},m_{a0})$
+  \subsection*{Bob acknowledges Alice's hello via HelloAck.}
+  $bob_1(p)$
+  \subsection*{Alice receives Bob's HelloAck}
+  $alice_1(p_{b1})$
+  \subsection*{Bob says Hello to Alice.}
+  $bob_2(p,v,c,h3,z,fs,hc,cc,ac,kc,sc,hs,cs,as,ks,ss,m)$
+  \subsection*{Alice receives Bob's Hello.}
+   $alice_2(p_{b2},v_{b2},c_{b2},h3_{b2},z_{b2},fs_{b2},hc_{a0}
+     ,cc_{b2},ac_{b2},kc_{b2},sc_{b2},hs_{b2},cs_{b2}
+          ,as_{b2},ks_{b2},ss_{b2},m_{b2})$
+  \subsection*{Alice acknowledges Bob's Hello via HelloAck.}
+  $alice_3(p)$
+  \subsection*{Bob receives Alice's HelloAck.}
+  $bob_3(p_{a3})$
+  \section*{The Commit and DHPart Messages.}
   test
-  \subsection{Messages}
-  \subsubsection{Hello}
-  Alice says hello to Bob.
-  \begin{align*}
-          alice_0(p, v, cid, h3, zid, flags, hashAlgs, 
-            cipherAlgs, authTags, keyAgreements, SAStypes, mac)
-  \end{align*}
 

### 2018-12-17 Src/paper.tex
Midway through formally documenting the DH process of ZRTP

--- 2018-12-15 Src/paper.tex
@@
 \maketitle
-
-\section*{A description of the ZRTP Protocol}
-  \subsection*{Syntax}
-  \subsubsection{$p$}
-  $p$ represents the message preamble $0x505a$ followed
-  by a 16-bit length in 32-bit words, followed by the message
-  type 2-word block string (e.g.) ``hello''.
-  \subsubsection{$v$}
-  $v$ represents the 4-character long string containing the
-  version of the ZRTP protocol.
-  \subsubsection{$cid$}
-  $cid$ represents the client identificationn string which
+  \section{The Message Preamble}
+  All ZRTP Messages are prefixed by a preamble, message length
+  and message type. 
+  \begin{itemize}
+  \item Let $p$ represent the message preamble $0x505a$ followed
+        by a 16-bit message length in 32-bit words, followed by the 
+        message type 2-word block string (e.g. ``hello'').
+  \end{itemize}
+  \section{The Hello Messages}
+  \begin{itemize}
+    \item Let $v$ represent the 4-character long string containing 
+          the version of the ZRTP protocol.
+    \item Let $c$ represent the client identification string which
           identifies the vendor and release of the ZRTP software.
-  \subsubsection($h3$)
-  $h3$ represents the following: \\
-    $h0$ representing a 256-bit random nonce. \\
-    $h1$ representing a hash of $h0$ with SHA-256.\\
-    $h2$ representing a hash of $h1$ with SHA-256.\\
-    $h3$ representing a hash of $h2$ with SHA-256.
-  \subsubsection($zid$)
+    \item Let $h3$ represent the following:
+       \begin{itemize}
+       \item Let $h0$ represent a 256-bit random nonce.
+       \item Let $h1$ represent a hash of $h0$ with SHA-256.
+       \item Let $h2$ represent a hash of $h1$ with SHA-256.
+       \item Let $h3$ represent a hash of $h2$ with SHA-256.
+       \end{itemize}
+    \item Let $z$ represent the 96-bit long unique identifier for 
+          the ZRTP endpoint. This is a random number generated at 
+          installation time to act as a key when looking up 
+          shared secrets in a local cache.
+    \item Let $fs$ represent a 4-bit long sequence of flags. 
+          The leading bit is 0, the second represents a 
+          signature-capable flag, the third a MiTM flag to 
+          identify that this message was sent from a PBX. The 
+          fourth and final bit represents a passive flag 
+          whichis only used on devices that send hello, 
+          but will never send commit messages.
+    \item Let $hc$ represent the number (count) of hashing 
+            algorithms.
+    \item Let $cc$ represent the number of cipher algorithms.
+    \item Let $ac$ represent the number of auth tag types.
+    \item Let $kc$ reresent the number of key agreement types.
+    \item Let $sc$ represent the number of SAS types.
+    \item Let $hs$ represent the ordered set of hashing algorithms.
+    \item Let $cs$ represent the set of cipher algorithms.
+    \item Let $as$ represent the set of SRTP auth tag types.
+    \item Let $ks$ represent the set of key agreement types.
+    \item Let $ss$ represents the set of short authentication 
+          string types.
+    \item Let $m$ represents the machine authentication code 
+          that finishes the ZRTP message.
+  \end{itemize}
+  \subsection*{Alice says Hello to Bob}
+   $alice_0(p,v,c,h3,z,fs,hc,cc,ac,kc,sc,hs,cs,as,ks,ss,m)$
+  \subsection*{Bob receives Alice's Hello}
+   $bob_0(p_{a0},v_{a0},c_{a0},h3_{a0},z_{a0},fs_{a0},hc_{a0}
+     ,cc_{a0},ac_{a0},kc_{a0},sc_{a0},hs_{a0},cs_{a0}
+          ,as_{a0},ks_{a0},ss_{a0},m_{a0})$
+  \subsection*{Bob acknowledges Alice's hello via HelloAck}
+  $bob_1(p)$
+  \subsection*{Alice receives Bob's HelloAck}
+  $alice_1(p_{b1})$
+  \subsection*{Bob says Hello to Alice}
+  $bob_2(p,v,c,h3,z,fs,hc,cc,ac,kc,sc,hs,cs,as,ks,ss,m)$
+  \subsection*{Alice receives Bob's Hello}
+   $alice_2(p_{b2},v_{b2},c_{b2},h3_{b2},z_{b2},fs_{b2},hc_{a0}
+     ,cc_{b2},ac_{b2},kc_{b2},sc_{b2},hs_{b2},cs_{b2}
+          ,as_{b2},ks_{b2},ss_{b2},m_{b2})$
+  \subsection*{Alice acknowledges Bob's Hello via HelloAck}
+  $alice_3(p)$
+  \subsection*{Bob receives Alice's HelloAck}
+  $bob_3(p_{a3})$
+  \section*{The Commit Message}
+  \begin{itemize}
+    \item Let $ha$ represent the negotiated hash algorithm.
+    \item Let $ca$ represent the negotiated cipher algorithm.
+    \item Let $at$ represent the negotiated auth-tag type.
+    \item Let $kt$ represent the negotiated key-agreement type.
+    \item Let $st$ represent the negotiated short authentication
+            string type.
+    \item Let $hvi$ represent the initatiors hash value where:
+      \begin{itemize}
+        \item Let $svi$ represent a random number.
+        \item Let $g$ represent the base.
+        \item Let $p$ represent the prime modulus.
+        \item $svi$, $g$, and $p$ are all functions of $kt$
+              such that: 
+        \item Let $pvi = mod(g^{svi},p)$
+        \item Let $||$ denote bitwise concatenation
+        \item Let $dh2i$ represent the initiators DH Part 2 Message.
+        \item Let $hellor$ represent the responders Hello Message.
+        \item $hvi = ha(dh2i || hellor)$
+      \end{itemize}
+  \end{itemize}
+  \subsection{Bob sends a Commit to Alice}
+  $bob_4(p,h2,z,ha,ca,at,kt,st,hvi,m)$
+  \subsection{Alice receives Bob's Commit}
   test
-  \subsection{Messages}
-  \subsubsection{Hello}
-  Alice says hello to Bob.
-  \begin{align*}
-          alice_0(p, v, cid, h3, zid, flags, hashAlgs, 
-            cipherAlgs, authTags, keyAgreements, SAStypes, mac)
-  \end{align*}
+  \section{The DH Part 2 Message}
 

### 2018-12-18 Src/paper.tex
Need to look into MAC and HMAC in order to properly determine hasing for DH-Part 2
Some more work on DH

@@
           string types.
+    %TODO: Figure out what m actually does.
     \item Let $m$ represents the machine authentication code 
@@
               such that: 
-        \item Let $pvi = mod(g^{svi},p)$
-        \item Let $||$ denote bitwise concatenation
+        \item Let $pvi = mod(g^{svi},p)$.
+        \item Let $||$ denote bitwise concatenation.
         \item Let $dh2i$ represent the initiators DH Part 2 Message.
@@
   \subsection{Alice receives Bob's Commit}
-  test
+  $alice_4(p_{b4},h2_{b4},z_{b4},ha_{b4},ca_{b4},at_{b4},kt_{b4}
+    ,st_{b4},hvi_{b4},m_{b4})$
+  \section{The DH Part 1 Message}
+  \begin{itemize}
+    \item Let $rstr$ represent a message denoting ``Responder''.
+    \item Let $s1r$ represent the responders first shared secret
+          if it exists, or null otherwise.
+    \item Let $s2r$ represent the responders second shared secret
+          if it exists, or null otherwise.
+    \item Let $rs1r = m(s1r,rstr)$ represent the non-invertible 
+          hash of the responders first retained shared secret.
+    \item Let $rs2r = m(m2r,rstr)$ represent the non-invertible
+          hash of the responders second retained shared secret.
+    \item Let $auxr$ represent the responders auxiliary shared 
+          secret.
+    \item Let $rh3$ represent the responder H3 value.
+    \item Let $asr = m(aux,rh3)$ represent the non-invertible hash
+          of the responders auxiliary shared secret.
+    \item Let $pbxr$ represent the responders pbx shared secret.
+    \item Let $psr = m(pbx,rstr)$ represent the non-invertible
+          hash of the responders pbx shared secret.
+    \item Let $pvr$ represent the responders hash value where:
+      \begin{itemize}
+        \item Let $svr$ represent a random number.
+        \item Let $g$ represent the base.
+        \item Let $p$ represent the prime modulus.
+        \item $svr$, $g$, and $p$ are all functions of $kt$
+              such that: 
+        \item Let $pvr = mod(g^{svr},p)$.
+        \item Let $||$ denote bitwise concatenation.
+        \item Let $dh2i$ represent the initiators DH Part 2 Message.
+        \item Let $hellor$ represent the responders Hello Message.
+        \item $hvi = ha(dh2i || hellor)$
+      \end{itemize}
+  \end{itemize}
+
   \section{The DH Part 2 Message}
+  \begin{itemize}
+    \item Let $istr$ represent a message denoting ``Initiator''.
+    \item Let $s1$ represent the initiators first shared secret if
+          it exists or null otherwise.
+    \item Let $s2$ represent the initiators second shared secret if
+          it exists or null otherwise.
+    \item Let $rs1 = m(s1,istr)$ represent the non-invertible hash 
+          of the initiators first retained shared secret.
+    \item Let $rs2 = m(s2,istr)$ represent the non-invertible hash
+          of the intiators second retained shared secret.
+    \item Let $aux$ represet the auxiliary shared secret.
+    \item Let $ih3$ represent the initiators H3 value.
+    \item Let $asi = m(aux,ih3)$ represent the non-invertible hash
+          of the initiators auxiliary shared secret.
+    \item Let $pbx$ represent the pbx shared secret.
+    \item Let $psi = m(pbx,istr)$ represent the non-invertible
+          hash of the initiators pbx shared secret.
+
+  \end{itemize}
 

### 2018-12-19 Src/paper.tex
More progress formalising DH exchange

@@
   \begin{itemize}
-  \item Let $p$ represent the message preamble $0x505a$ followed
+  \item Let $pr$ represent the message preamble $0x505a$ followed
         by a 16-bit message length in 32-bit words, followed by the 
@@
   \subsection*{Alice says Hello to Bob}
-   $alice_0(p,v,c,h3,z,fs,hc,cc,ac,kc,sc,hs,cs,as,ks,ss,m)$
+   $alice_0(pr,v,c,h3,z,fs,hc,cc,ac,kc,sc,hs,cs,as,ks,ss,m)$
   \subsection*{Bob receives Alice's Hello}
-   $bob_0(p_{a0},v_{a0},c_{a0},h3_{a0},z_{a0},fs_{a0},hc_{a0}
+   $bob_0(pr_{a0},v_{a0},c_{a0},h3_{a0},z_{a0},fs_{a0},hc_{a0}
      ,cc_{a0},ac_{a0},kc_{a0},sc_{a0},hs_{a0},cs_{a0}
@@
   \subsection*{Bob acknowledges Alice's hello via HelloAck}
-  $bob_1(p)$
+  $bob_1(pr)$
   \subsection*{Alice receives Bob's HelloAck}
-  $alice_1(p_{b1})$
+  $alice_1(pr_{b1})$
   \subsection*{Bob says Hello to Alice}
-  $bob_2(p,v,c,h3,z,fs,hc,cc,ac,kc,sc,hs,cs,as,ks,ss,m)$
+  $bob_2(pr,v,c,h3,z,fs,hc,cc,ac,kc,sc,hs,cs,as,ks,ss,m)$
   \subsection*{Alice receives Bob's Hello}
-   $alice_2(p_{b2},v_{b2},c_{b2},h3_{b2},z_{b2},fs_{b2},hc_{a0}
+   $alice_2(pr_{b2},v_{b2},c_{b2},h3_{b2},z_{b2},fs_{b2},hc_{a0}
      ,cc_{b2},ac_{b2},kc_{b2},sc_{b2},hs_{b2},cs_{b2}
@@
   \subsection*{Alice acknowledges Bob's Hello via HelloAck}
-  $alice_3(p)$
+  $alice_3(pr)$
   \subsection*{Bob receives Alice's HelloAck}
-  $bob_3(p_{a3})$
+  $bob_3(pr_{a3})$
   \section*{The Commit Message}
@@
   \end{itemize}
-  \subsection{Bob sends a Commit to Alice}
-  $bob_4(p,h2,z,ha,ca,at,kt,st,hvi,m)$
-  \subsection{Alice receives Bob's Commit}
-  $alice_4(p_{b4},h2_{b4},z_{b4},ha_{b4},ca_{b4},at_{b4},kt_{b4}
-    ,st_{b4},hvi_{b4},m_{b4})$
-  \section{The DH Part 1 Message}
+  \subsection*{Bob prepares a DH Part 2 Message}
+  $bob_4(pr,h1,rs1i,rs2i,asi,psi,pvi,m)$
+  \subsection*{Bob sends a Commit to Alice}
+  $bob_5(pr,h2,z,ha,ca,at,kt,st,hvi,m)$
+  \subsection*{Alice receives Bob's Commit}
+  $alice_4(pr_{b5},h2_{b5},z_{b5},ha_{b5},ca_{b5},at_{b5},kt_{b5}
+    ,st_{b5},hvi_{b5},m_{b5})$
+  \section*{The DH Part 1 Message}
   \begin{itemize}
@@
     \item Let $rh3$ represent the responder H3 value.
-    \item Let $asr = m(aux,rh3)$ represent the non-invertible hash
+    \item Let $asr = m(auxr,rh3)$ represent the non-invertible hash
           of the responders auxiliary shared secret.
@@
         \item Let $pvr = mod(g^{svr},p)$.
-        \item Let $||$ denote bitwise concatenation.
-        \item Let $dh2i$ represent the initiators DH Part 2 Message.
-        \item Let $hellor$ represent the responders Hello Message.
-        \item $hvi = ha(dh2i || hellor)$
       \end{itemize}
   \end{itemize}
-
-  \section{The DH Part 2 Message}
+  \subsection*{Alice sends DH Part 1 to Bob}
+  $alice_5=(pr,h1,rs1r,rs2r,asr,psr,pvr,m)$
+  \subsection*{Bob receives Alice's DH Part 1}
+  $bob_6=(pr_{a5},h1_{a5},rs1r_{a5},rs2r_{a5},asr_{a5},psr_{a5},
+           pvr_{a5},m_{a5})$
+  \subsection*{Bob checks Alice's DH Part 1 and calculates DH 
+               Result}
+  \begin{itemize}
+    \item if $pvr_{a5} = p_{b5}$ or $pvr_{a5} = p_{b5} - 1$ then 
+          terminate protocol. Otherwise continue:
+    \item Let $dhr = mod(pvr_{a5}^{svi_{b5}},p)$ represent the 
+          DH result.
+  \end{itemize}
+  \section*{The DH Part 2 Message}
   \begin{itemize}
@@
           it exists or null otherwise.
-    \item Let $rs1 = m(s1,istr)$ represent the non-invertible hash 
+    \item Let $rs1i = m(s1,istr)$ represent the non-invertible hash 
           of the initiators first retained shared secret.
-    \item Let $rs2 = m(s2,istr)$ represent the non-invertible hash
+    \item Let $rs2i = m(s2,istr)$ represent the non-invertible hash
           of the intiators second retained shared secret.
-    \item Let $aux$ represet the auxiliary shared secret.
+    \item Let $auxi$ represet the auxiliary shared secret.
     \item Let $ih3$ represent the initiators H3 value.
-    \item Let $asi = m(aux,ih3)$ represent the non-invertible hash
+    \item Let $asi = m(auxi,ih3)$ represent the non-invertible hash
           of the initiators auxiliary shared secret.
-    \item Let $pbx$ represent the pbx shared secret.
+    \item Let $pbxi$ represent the pbx shared secret.
     \item Let $psi = m(pbx,istr)$ represent the non-invertible
           hash of the initiators pbx shared secret.
-
   \end{itemize}
-
+  \subsection{Bob sends DH Part 2 to Alice}
+  $bob_7 = bob_4$
+  \subsubsection{Alice receives Bob's DH Part 2}
+  $alice_6(pr_{b7},h1_{b7},rs1i_{b7},rs2i_{b7},asi_{b7},
+           psi_{b7},pvi_{b7},m_{b7})$
+  \subsection*{Alice checks Bob's DH Part 2 and calculates DH 
+               Result}
+  \begin{itemize}
+    \item if $pvi_{b7} = p_{a5}$ or $pvr_{b7} = p_{a5} - 1$ then 
+          terminate protocol. Otherwise continue:
+    \item if $hash(bob_7 || alice_0) \neq hvi_b5$ then terminate 
+          protocol. Otherwise continue:
+    \item Let $dhr = mod(pvr_{b7}^{svi_{a5}},p)$ represent the 
+          DH result.
+  \end{itemize}
 \end{document}

### 2018-12-20 Src/paper.tex
Some work towards describing a simplified protocol

@@
 \maketitle
-  \section{The Message Preamble}
+  \section{A description of the ZRTP Protocol up to public key 
+           exposure.}
+  \subsection{The Message Preamble}
   All ZRTP Messages are prefixed by a preamble, message length
@@
   \end{itemize}
-  \subsection*{Alice says Hello to Bob}
+  \subsubsection{Alice says Hello to Bob}
    $alice_0(pr,v,c,h3,z,fs,hc,cc,ac,kc,sc,hs,cs,as,ks,ss,m)$
-  \subsection*{Bob receives Alice's Hello}
+  \subsubsection{Bob receives Alice's Hello}
    $bob_0(pr_{a0},v_{a0},c_{a0},h3_{a0},z_{a0},fs_{a0},hc_{a0}
@@
           ,as_{a0},ks_{a0},ss_{a0},m_{a0})$
-  \subsection*{Bob acknowledges Alice's hello via HelloAck}
+  \subsubsection{Bob acknowledges Alice's hello via HelloAck}
   $bob_1(pr)$
-  \subsection*{Alice receives Bob's HelloAck}
+  \subsubsection{Alice receives Bob's HelloAck}
   $alice_1(pr_{b1})$
-  \subsection*{Bob says Hello to Alice}
+  \subsubsection{Bob says Hello to Alice}
   $bob_2(pr,v,c,h3,z,fs,hc,cc,ac,kc,sc,hs,cs,as,ks,ss,m)$
-  \subsection*{Alice receives Bob's Hello}
+  \subsubsection{Alice receives Bob's Hello}
    $alice_2(pr_{b2},v_{b2},c_{b2},h3_{b2},z_{b2},fs_{b2},hc_{a0}
@@
           ,as_{b2},ks_{b2},ss_{b2},m_{b2})$
-  \subsection*{Alice acknowledges Bob's Hello via HelloAck}
+  \subsubsection{Alice acknowledges Bob's Hello via HelloAck}
   $alice_3(pr)$
-  \subsection*{Bob receives Alice's HelloAck}
+  \subsubsection{Bob receives Alice's HelloAck}
   $bob_3(pr_{a3})$
-  \section*{The Commit Message}
+  \subsection{The Commit Message}
   \begin{itemize}
@@
   \end{itemize}
-  \subsection*{Bob prepares a DH Part 2 Message}
+  \subsubsection{Bob prepares a DH Part 2 Message}
   $bob_4(pr,h1,rs1i,rs2i,asi,psi,pvi,m)$
-  \subsection*{Bob sends a Commit to Alice}
+  \subsubsection{Bob sends a Commit to Alice}
   $bob_5(pr,h2,z,ha,ca,at,kt,st,hvi,m)$
-  \subsection*{Alice receives Bob's Commit}
+  \subsubsection{Alice receives Bob's Commit}
   $alice_4(pr_{b5},h2_{b5},z_{b5},ha_{b5},ca_{b5},at_{b5},kt_{b5}
     ,st_{b5},hvi_{b5},m_{b5})$
-  \section*{The DH Part 1 Message}
+  \subsection{The DH Part 1 Message}
   \begin{itemize}
@@
   \end{itemize}
-  \subsection*{Alice sends DH Part 1 to Bob}
+  \subsubsection{Alice sends DH Part 1 to Bob}
   $alice_5=(pr,h1,rs1r,rs2r,asr,psr,pvr,m)$
-  \subsection*{Bob receives Alice's DH Part 1}
+  \subsubsection{Bob receives Alice's DH Part 1}
   $bob_6=(pr_{a5},h1_{a5},rs1r_{a5},rs2r_{a5},asr_{a5},psr_{a5},
            pvr_{a5},m_{a5})$
-  \subsection*{Bob checks Alice's DH Part 1 and calculates DH 
+  \subsubsection{Bob checks Alice's DH Part 1 and calculates DH 
                Result}
@@
   \end{itemize}
-  \section*{The DH Part 2 Message}
+  \subsection{The DH Part 2 Message}
   \begin{itemize}
@@
   \end{itemize}
-  \subsection{Bob sends DH Part 2 to Alice}
+  \subsubsection{Bob sends DH Part 2 to Alice}
   $bob_7 = bob_4$
@@
            psi_{b7},pvi_{b7},m_{b7})$
-  \subsection*{Alice checks Bob's DH Part 2 and calculates DH 
+  \subsubsection{Alice checks Bob's DH Part 2 and calculates DH 
                Result}
@@
   \end{itemize}
+  \section{A Simplification of ZRTP}
+  \subsection{Negotiated Protocols}
+  To simplify the formal verification of timing observability, 
+  this simplified protocol will forgo the agreement process between
+  the parties and all parties will assume the following:
+  \begin{itemize}
+    \item Let $ha$ represent the agreed-upon hash algorithm 
+          SHA-256.
+    \item Let $ca$ represent the agreed-upon cipher algorithm 
+          AES-1.
+    \item Let $at$ represent the agreed-upon auth tag type
+          HS32 - based on HMAC-SHA1 in RFC 3711.
+    \item Let $kt$ represent the agreed-upon key agreement
+          type DH2k, p=2048 Bit Prime as per RFC 3526.
+    \item Let $st$ represent the agreed-upon short authentication
+          string type B32
+  \end{itemize}
+  \subsubsection{The Hello and HelloAck Messages}
+  If this protocol assumes pre-agreement on protocol parameters
+  by Alice and Bob, and assumes that both Alice and Bob pre-compute
+  $h0$, $h1$, $h2$, and $h3$ then the ``Hello'' messages and the 
+  corresponding ``HelloAck'' messages can be considered to have
+  a constant time, and thus possibly be ommited for the purpose of
+  verifying timing observability.
 \end{document}

### 2018-12-20 Src/paper.tex
Updated simplified model of ZRTP, still need to write up DH Part 1 and 2 though!

@@
   \end{itemize}
+  \newpage
   \section{A Simplification of ZRTP}
+  This section details a simplified model of the ZRTP protocol with the
+  purpose of identifying relevant computation for timing observability.
   \subsection{Negotiated Protocols}
@@
     \item Let $kt$ represent the agreed-upon key agreement
-          type DH2k, p=2048 Bit Prime as per RFC 3526.
+          type DH3k, p=3072 Bit Prime as per RFC 3526 section 4.
     \item Let $st$ represent the agreed-upon short authentication
@@
   \end{itemize}
-  \subsubsection{The Hello and HelloAck Messages}
+  \subsection{The Hello and HelloAck Messages}
   If this protocol assumes pre-agreement on protocol parameters
@@
   a constant time, and thus possibly be ommited for the purpose of
-  verifying timing observability.
+  timing observability. \\
+  while $h3$ can be precalculated, it is important for the responder
+  to send this to the initiator as this allows the responder to validate
+  against the initiators DH Part 2 message.
+  \begin{itemize}
+    \item Let $h0$ represent a 256 bit random nonce.
+    \item Let $h1$ represent SHA-256 of $h0$
+    \item Let $h2$ represent SHA-256 of $h1$
+    \item Let $h3$ represent SHA-256 of $h2$
+  \end{itemize}
+  \subsubsection{Alice sends Hello}
+  $alice_0(h3_{a0})$
+  \subsubsection{Bob sends Hello}
+  $bob_0(h3_{b0})$
+  \subsection{The Commit Message}
+  Given the assumptions above, the commit message contains the following
+  components that are required to be computed by the initiator.
+  \begin{itemize}
+    \item Let $hvi$ represent the initiators hash value under DH3k key
+      agreement type, such that:
+      \begin{itemize}
+        \item Let $svi$ represent a random 3072 bit number under the DH3k key
+              agreement type.
+        \item Let $p = 2^{3072} - 2^3008 - 1 + 2^64(2^2942\pi + 1690314)$ represent
+              the prime number under the DH3k key agreement type.
+        \item Let $g = 2$ represent the generator under the DH3k key agreement
+              type.
+        \item Let $pvi = mod(g^svi, p)$ represent the public value of the
+              initiator.
+        \item Let $dh2i$ represent the precalculation of the DH Part 2 message
+              by the initator in order to compute part of the $hvi$.
+        \item Let $h3_{a0}$ represent Alice's Hello message that Bob has
+              received.
+        \item Let $||$ denote bitwise concatenation.
+        \item Then $hvi = ha(dh2i||h3_{a0})$ 
+      \end{itemize}
+  \end{itemize}
+  \subsubsection{Bob precalculates DH Part 2}
+  $bob_1=(h3_{b0},pvi)$
+  \subsubsection{Bob sends a Commit to Alice}
+  $bob_2(h2_{b1},hvi)$
 \end{document}

### 2018-12-20 Src/paper.tex
Finished initial modelling of simplified protocol

@@
           fourth and final bit represents a passive flag 
-          whichis only used on devices that send hello, 
+          which is only used on devices that send hello, 
           but will never send commit messages.
@@
     \item Let $ac$ represent the number of auth tag types.
-    \item Let $kc$ reresent the number of key agreement types.
+    \item Let $kc$ represent the number of key agreement types.
     \item Let $sc$ represent the number of SAS types.
@@
             string type.
-    \item Let $hvi$ represent the initatiors hash value where:
+    \item Let $hvi$ represent the initiators hash value where:
       \begin{itemize}
@@
         \item Let $pvi = mod(g^{svi},p)$.
-        \item Let $||$ denote bitwise concatenation.
+        \item Let $||$ denote bit-wise concatenation.
         \item Let $dh2i$ represent the initiators DH Part 2 Message.
@@
     \item Let $rs2i = m(s2,istr)$ represent the non-invertible hash
-          of the intiators second retained shared secret.
-    \item Let $auxi$ represet the auxiliary shared secret.
+          of the initiators second retained shared secret.
+    \item Let $auxi$ represent the auxiliary shared secret.
     \item Let $ih3$ represent the initiators H3 value.
@@
   corresponding ``HelloAck'' messages can be considered to have
-  a constant time, and thus possibly be ommited for the purpose of
+  a constant time, and thus possibly be omitted for the purpose of
   timing observability. \\
-  while $h3$ can be precalculated, it is important for the responder
+  while $h3$ can be pre-calculated, it is important for the responder
   to send this to the initiator as this allows the responder to validate
@@
   $bob_0(h3_{b0})$
-  \subsection{The Commit Message}
+  \subsection{The Commit Message} \label{commit}
   Given the assumptions above, the commit message contains the following
@@
               initiator. 
-        \item Let $dh2i$ represent the precalculation of the DH Part 2 message
-              by the initator in order to compute part of the $hvi$.
+        \item Let $dh2i$ represent the calculation of the DH Part 2 message
+              by the initiator in order to compute part of the $hvi$.
         \item Let $h3_{a0}$ represent Alice's Hello message that Bob has
               received.
-        \item Let $||$ denote bitwise concatenation.
+        \item Let $||$ denote bit-wise concatenation.
         \item Then $hvi = ha(dh2i||h3_{a0})$ 
@@
   \end{itemize}
-  \subsubsection{Bob precalculates DH Part 2}
-  $bob_1=(h3_{b0},pvi)$
+  \subsubsection{Bob pre-calculates DH Part 2}
+  $bob_1=(h1_{b0},pvi)$
   \subsubsection{Bob sends a Commit to Alice}
   $bob_2(h2_{b1},hvi)$
+  \subsection{The DH Part 1 Message}
+  The DH Part 1 message is composed primarily of book keeping parameters
+  regarding previous shared secrets between the responder and initiator. These
+  details will be omitted in this simplified model in the interest of brevity as
+  they do not require any computing beyond a simple looking and hash.
+  \begin{itemize}
+    \item Let $pvr$ represent the responders public hash value under the DH3k
+      key agreement type where:
+      \begin{itemize}
+        \item Let $svr$ represent a random 3072 bit number under the DH3k key
+              agreement type.
+        \item Let $p = 2^{3072} - 2^3008 - 1 + 2^64(2^2942\pi + 1690314)$ represent
+              the prime number under the DH3k key agreement type.
+        \item Let $g = 2$ represent the generator under the DH3k key agreement
+              type.
+        \item Let $pvr = mod(g^svr, p)$ represent the public value of the
+              initiator.
+      \end{itemize}
+  \end{itemize}
+  \subsubsection{Alice sends DH Part 1 to Bob}
+  $alice_1(h1_{a0},pvr)$
+
+  \subsubsection{Bob calculates the DH Result.}
+  \[
+    bob_3(pvr_{a1},svi_{b1},p_{b1})=
+    \begin{cases}
+      \text{Terminate Protocol}, &\text{if } pvr_{a1} = p_{b1} \\
+      \text{Terminate Protocol}, &\text{otherwise if } pvr_{a1} = p_{b1} - 1 \\
+      \text{Let $dhr = mod(pvr_{a1}^{svi_{b1}},p)$}, &\text{otherwise.}
+    \end{cases}
+  \]
+  \subsection{The DH Part 2 Message}
+  This message is a mirror of the DH Part 1 Message from the initiators
+  viewpoint. The calculation of the $pvi$ is covered under section
+  \ref{commit}.
+
+  \subsubsection{Bob sends DH Part 2 to Alice}
+  $bob_4(h2_{b0},pvi_{b1})$
+
+  \subsubsection{Alice calculates the DH Result.}
+  \[
+    alice_2(pvr_{a1},svi_{b1},p_{b1})=
+    \begin{cases}
+      \text{Terminate Protocol}, &\text{if } pvr_{a1} = p_{b1} \\
+      \text{Terminate Protocol}, &\text{otherwise if } pvr_{a1} = p_{b1} - 1 \\
+      \text{Terminate Protocol}, &\text{otherwise if } ha(bob_4||alice_0) \neq
+      hvi_{b2} \\
+      \text{Let $dhr = mod(pvr_{a1}^{svi_{b1}},p)$}, &\text{otherwise.}
+    \end{cases}
+  \]
+
 \end{document}

### 2019-01-09 Src/paper.tex
Added syntax for prg language and detailed the setup of sha-256 in prg

@@
               agreement type.
-        \item Let $p = 2^{3072} - 2^3008 - 1 + 2^64(2^2942\pi + 1690314)$ represent
+      \item Let $p = 2^{3072} - 2^{3008} - 1 + 2^{64}(2^{2942}\pi + 1690314)$ represent
               the prime number under the DH3k key agreement type.
@@
       \text{Terminate Protocol}, &\text{if } pvr_{a1} = p_{b1} \\
-      \text{Terminate Protocol}, &\text{otherwise if } pvr_{a1} = p_{b1} - 1 \\
-      \text{Terminate Protocol}, &\text{otherwise if } ha(bob_4||alice_0) \neq
-      hvi_{b2} \\
-      \text{Let $dhr = mod(pvr_{a1}^{svi_{b1}},p)$}, &\text{otherwise.}
+      \text{Terminate Protocol}, &\text{otherwise if } pvr_{a1} = 
+            p_{b1} - 1 \\
+      \text{Terminate Protocol}, &\text{otherwise if } 
+            ha(bob_4||alice_0) \neq hvi_{b2} \\
+      \text{Let $dhr = mod(pvr_{a1}^{svi_{b1}},p)$}, 
+            &\text{otherwise.} 
     \end{cases}
@@
 
+  \section{A Prototype Domain Specific Language}
+  \subsection{Values}
+  A value $v$ is given by the following: \\
+  let $b32$ represent a 32 bit integer. \\
+  \begin{align*}
+  v\; ::=\; &val(b32) \\
+          &|\; add(v_1,v_2) \\
+          &|\; sub(v_1,v_2) \\
+          &|\; xor(v_1,v_2) \\
+          &|\; rightrotate(v_1,v_2) \\
+          &|\; rightshift(v_1,v_2)
+  \end{align*}
+  \subsection{\textit{Prg}: a DSL for the constrained protocol.}
+  let $n$ represent a natural number. \\
+  let $v$ represent the value type. \\
+  let $s$ represent the string type. \\
+  let $vec(n, t)$ represent the vector type of length $n$ of 
+    values of type $t$.
+  \begin{align*}
+  prg(n)\; ::=\; &\text{Terminate: } \\
+                 &halt : prg(1) \\
+                 &\text{Assign a constant: } \\
+                 &|\; assc(name:s,val:v,cont:prg(k)) 
+                        : prg (k + 1) \\
+                 &\text{Assign an array: } \\
+                 &|\; assa(name:s,vals : vec(size, v), cont:prg(k))
+                        : prg (k + size + 1) \\
+                 &\text{Conditional branching: } \\
+                 &|\; cond(pred : prg(n), true : prg(m),
+                        false : prg(m), cont: prg(k)) 
+                        : prg(k + m + n + 1) \\
+                 &\text{Repetition: } \\
+                 &|\; do(counts : n, iter : prg(k), cont : prg(m))
+                        : prg(k * n + m) \\
+                 &\text{Do nothing: } \\
+                 &|\; skip(cont : prg(k)) : prg(k + 1)
+  \end{align*}
+
+  \subsection{Describing SHA-256}
+  \subsubsection{Initialising the hash values:}
+  \begin{align*}
+  \text{let $hs : vec(8, v)$ represent } 
+          [&val(6a09e667),val(bb67ae85), val(3c6ef372), \\
+           &val(a54ff53a),val(510e527f), val(9b05688c), \\
+           &val(1f83d9ab),val(5be0cd19)].
+  \end{align*}
+  $initHashValue : prg(n) \mapsto prg(n + 8 + 1)$ \\
+  $initHashValue(p) = assa(``hs",hs,p)$
+  \subsubsection{Initialising the round constants:}
+  \begin{align*}
+  \text{let $ks : vec(64,v)$ represent }
+          [&val(428a2f98),val(71374491),val(b5c0fbcf), \\
+           &val(e9b5dba5),val(3956c25b),val(59f111f1), \\
+           &val(923f82a4),val(ab1c5ed5), \\
+           &val(d807aa98),val(12835b01),val(243185be), \\
+           &val(550c7dc3),val(72be5d74),val(80deb1fe), \\
+           &val(9bdc06a7),val(c19bf174), \\
+           &val(e49b69c1),val(efbe4786),val(0fc19dc6), \\
+           &val(240ca1cc),val(2de92c6f),val(4a7484aa), \\
+           &val(5cb0a9dc),val(76f988da), \\
+           &val(983e5152),val(a831c66d),val(b00327c8), \\
+           &val(bf597fc7),val(c6e00bf3),val(d5a79147), \\
+           &val(06ca6351),val(14292967), \\
+           &val(27b70a85),val(2e1b2138),val(4d2c6dfc), \\
+           &val(53380d13),val(650a7354),val(766a0abb), \\
+           &val(81c2c92e),val(92722c85), \\
+           &val(a2bfe8a1),val(a81a664b),val(c24b8b70), \\
+           &val(c76c51a3),val(d192e819),val(d6990624), \\
+           &val(f40e3585),val(106aa070), \\
+           &val(19a4c116),val(1e376c08),val(2748774c), \\
+           &val(34b0bcb5),val(391c0cb3),val(4ed8aa4a), \\
+           &val(5b9cca4f),val(682e6ff3), \\
+           &val(748f82ee),val(78a5636f),val(84c87814), \\
+           &val(8cc70208),val(90befffa),val(a4506ceb), \\
+           &val(bef9a3f7),val(c67178f2)]
+  \end{align*}
+  $initRoundConsts : prg(n) \mapsto prg (n + 64 + 1)$ \\
+  $initRoundConsts(p) = assa(``ks",ks,p)$
+  \subsubsection{Padding the original message.}
+  \begin{align*}
+  \text{let $ps(ms) : vec(8,v) \mapsto vec(16,v)$ represent } 
+          [&ms_0,ms_1, ms_2, ms_3, ms_4, ms_5, ms_6, ms_7 \\
+           &val(80000000),val(00000000),val(00000000), \\
+           &val(00000000),val(00000000),val(00000000), \\
+           &val(00000000),val(00000100)]
+  \end{align*}
+  $pad256 : vec(8,v) \mapsto prg(n) \mapsto prg(n + 16 + 1)$ \\
+  $pad256(ms,p) = assa(``ms",ps(ms),p)$
+
 \end{document}

### 2019-01-16 Src/talk.tex
First rough draft of ASD half day presentation

\documentclass{beamer}
\usepackage[utf8]{inputenc}

\usepackage{minted}
\usepackage{pgf}
\usepackage{tikz}
\usepackage{upquote}
\usepackage{hyperref}
\usepackage{graphicx}
\usetikzlibrary{arrows,automata,positioning}

\setbeamertemplate{footline}[frame number]
\setbeamertemplate{navigation symbols}{}

\title{Verified Time Balancing of Securit Protocols}
\author{Donovan Crichton}
\date{January 2019}

\begin{document}

\frame{\titlepage}

\begin{frame}[fragile]
  \frametitle{The Problem}
  \begin{itemize}
    \item Can we formally prove that an implementation of
            a network security protocol is immune to 
                  timing side-channel attacks?
    \item In other words, can we show that a model of the protocol,
            along with its implementation is unable to leak
                  any timing information to an observer.
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Rationale}
  \begin{itemize}
    \item Some departments in the ASD spend a large amount of time
            manually verifying cryptographic routines in vendor
            code.
    \item Requires large amounts of time and expertise, resulting
            in a slow verfication process.
    \item Formal methods may allow the 
            automation of these verification processes.
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Formal Methods}
    \begin{itemize}
      \item A mathematical approach to the 
              development, specification and verification of 
                    software.
      \item Uses "theorem proving assistants", software that
              formally verifies against a specification.
      \item We can implement a proof of concept network security 
              protocol inside a theorem prover (namely Idris).
    \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{How do proof assistants work?}
    \begin{itemize}
      \item Rely on on a relationship between proofs in mathematics
              and computer programs known as the Curry-Howard 
                    correspondance.
      \item The proof system of intuitionistic 
              natural deduction can be directly interpreted 
                    as a model of computation known as 
                    lambda calculus.
    \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{A quick Idris example.}
  \begin{block}{A simple function in Idris}
  \begin{minted}{haskell}
f : Nat -> Nat
f x = x + 2
  \end{minted}
  \end{block}
  \begin{block}{The same function in familiar notation.}
$f : \mathbb{N} \mapsto \mathbb{N}$ \\
$f(x) = x + 2$
  \end{block}
\end{frame}

\begin{frame}[fragile]
 \frametitle{Logic in the Idris language.}
    \begin{table}[h!]
    \begin{tabular}{c|c|c|c}
    \textbf{Logic Term} & \textbf{Logic Symbol} & 
            \textbf{Idris Symbol} & \textbf{Idris Term} \\
    \hline
      Implication & p $\Rightarrow$ q & p \mintinline{haskell}{->} q
      & Arrow \\
      Conjunction & p $\land$ q & \mintinline{haskell}{(p, q)}
      & Pair (Product) \\ 
      Disjunction & p $\lor$ q & \mintinline{haskell}{Either p q}
      & Enum (Sum)\\
      Negation & $\lnot$ p & \mintinline{haskell}{p -> Void} &
      Void Type \\ 
      IFF/Eq & p $\equiv$ q, p $\iff$ q & \mintinline{haskell}{(p -> q, q -> p)}  
      & Pair Arrows \\
      Universal & $\forall$ x. P x &
      \mintinline{haskell}{p -> Type} & $\Pi$ Type \\
      Existential & $\exists$ x. P x
      & \mintinline{haskell}{(x ** P x)} & $\Sigma$ Type \\
      \hline
       & & \mintinline{haskell}{p = q} & Type Equality
    \end{tabular}
  \end{table}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Outline of the problem.}
  \begin{itemize}
  \item It's much simpler to prove properties for a small
        language than a large one.
  \item We can then design a minimal programming language
        that is just powerful enough to express our example 
        protocol, while proving that this language has
        the properties we desire.
  \item We could then design a provably correct translation
        from this language into one more amenable to 
        production (C, Assembly, etc).
\end{frame}

\begin{frame}[fragile]
  \frametitle{Prg : A minimal core language}
  \begin{item} Every expression in this language is paramterised
          over its supposed running time. 
  \begin{item} The language can be elaborated into a language nicer
          to use.
  \begin{item} The language can also be compiled or translated
          into a language more amenable for real-life performance.
\end{frame}

\begin{frame}[fragile]
  \frametitle{A diagram of Prg.}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Challenges and Outcomes}
  \begin{itemize}
    \item Still in the process of confirming whether Prf is 
            expressive enough for a cryptographic key exchange
    \item Are there other kinds of proofs we might be interested in
            on this language to ensure no additional leakage of
                  information?
    \item For future work, the implementation of the compilation
            or translation step in the thorem prover.
\end{frame}

%\begin{frame}[fragile]

%\end{frame}

\end{document}

### 2019-01-16 Src/talk.tex
Need to look at prf for Do, and how to manage arrays

@@
                   any timing information to an observer.
+    \item Some Example?
   \end{itemize}
@@
             in a slow verfication process.
-    \item Formal methods may allow the 
+    \item Formal methods may allow progress towards the 
             automation of these verification processes.
@@
               natural deduction can be directly interpreted 
-                    as a model of computation known as 
-                    lambda calculus.
+                    as a model of computation (lambda calculus).
     \end{itemize}
@@
 \begin{frame}[fragile]
-  \frametitle{A diagram of Prg.}
+  \frametitle{A diagram of Prg syntax.}
+   How should I represent this?
 \end{frame}
+
+\begin{frame}[fragile]
 

### 2019-01-19 Src/talk.tex
more work on talk. Just need to describe Prg pictorially and then demonstrate syntax!

--- 2019-01-16 Src/talk.tex
@@
 
-\title{Verified Time Balancing of Securit Protocols}
+\title{Verified Time Balancing of Security Protocols}
 \author{Donovan Crichton}
@@
 \begin{frame}[fragile]
-  \frametitle{The Problem}
+  \frametitle{Motivation}
   \begin{itemize}
-    \item Can we formally prove that an implementation of
-            a network security protocol is immune to 
-                  timing side-channel attacks?
-    \item In other words, can we show that a model of the protocol,
-            along with its implementation is unable to leak
-                  any timing information to an observer.
+    \item ASD manually verifies vendor code with containing cryptographic
+            processes.
+    \item Formal Methods: A mathematically based approach to the
+            specification and verification of software.
+    \item Can we reduce some of the resources ASD spends on 
+            manual verification by replacing with automatic verification?
+    \item A case study.
   \end{itemize}
@@
 \begin{frame}[fragile]
-  \frametitle{Rationale}
+  \frametitle{Formally Verifying a Time Balanced Security Protocol}
   \begin{itemize}
-    \item Some departments in the ASD spend a large amount of time
-            manually verifying cryptographic routines in vendor
-            code.
-    \item Requires large amounts of time and expertise, resulting
-            in a slow verfication process.
-    \item Formal methods may allow the 
-            automation of these verification processes.
+    \item Attackers can gain information from message timing.
+    \item Can we model this invariant? Naively all operations have the
+            same running time.
+    \item Can we ensure that assumptions on this model hold for the
+            implementation?
   \end{itemize}
@@
 \begin{frame}[fragile]
-  \frametitle{Formal Methods}
+  \frametitle{The ZRTP Protocol}
   \begin{itemize}
-      \item A mathematical approach to the 
-              development, specification and verification of 
-                    software.
-      \item Uses "theorem proving assistants", software that
-              formally verifies against a specification.
-      \item We can implement a proof of concept network security 
-              protocol inside a theorem prover (namely Idris).
+    \item Initially started with ZRTP.
+    \item ZRTP is complex and makes many decisions.
+    \item Simplified version that contains just enough detail to 
+            allow us to attempt to prove some interesting things!
   \end{itemize}
@@
 \begin{frame}[fragile]
-  \frametitle{How do proof assistants work?}
+  \frametitle{The Simplified Protocol}
     \begin{itemize}
-      \item Rely on on a relationship between proofs in mathematics
-              and computer programs known as the Curry-Howard 
-                    correspondance.
-      \item The proof system of intuitionistic 
-              natural deduction can be directly interpreted 
-                    as a model of computation known as 
-                    lambda calculus.
+      \item Commit messages contain hashes of 256 bit random nonce.
+      \item Diffie-Hellman key exchange contains modulo arithmetic.
+      \item How can we formally guarantee the timing of operations?
     \end{itemize}
@@
 \begin{frame}[fragile]
-  \frametitle{A quick Idris example.}
-  \begin{block}{A simple function in Idris}
-  \begin{minted}{haskell}
-f : Nat -> Nat
-f x = x + 2
-  \end{minted}
-  \end{block}
-  \begin{block}{The same function in familiar notation.}
-$f : \mathbb{N} \mapsto \mathbb{N}$ \\
-$f(x) = x + 2$
-  \end{block}
+  \frametitle{Approach}
+  \begin{itemize}
+    \item We can use the notion of propositions as types.
+    \item Dependently typed functional programming languages
+            also act as theorem provers for a higher-order
+                  constructive logic.
+    \item We can model this protocol in such a language, Idris.
+    \item We can express proofs about properties of the protocol.
+  \end{itemize}
 \end{frame}
@@
 \begin{frame}[fragile]
- \frametitle{Logic in the Idris language.}
+  \frametitle{Quick Background 1 - Currying}
+  All functions treated as taking a single argument. \\ \\
+  $f : \mathbb{N} \rightarrow \mathbb{N} \rightarrow \mathbb{N}$ \\
+  $f = + $ \\ \\
+  Applying an argument to a multi argument function returns the 
+  rest of the function! \\ \\
+  $f(2) : \mathbb{N} \rightarrow \mathbb{N}$ \\
+  $f(2) = 2 + $ \\ \\
+  Finally all arguments are applied. \\ \\
+  $f(2, 3) : \mathbb{N}$ \\
+  $f(2, 3) = 2 + 3 = 5 $
+\end{frame}
+
+\begin{frame}[fragile]
+  \frametitle{Quick Background 2 - Propositions as Types}
      \begin{table}[h!]
     \begin{tabular}{c|c|c|c}
-    \textbf{Logic Term} & \textbf{Logic Symbol} & 
-            \textbf{Idris Symbol} & \textbf{Idris Term} \\
+    \textbf{Logic Term} & \textbf{Logic Symbol} & \textbf{Idris Symbol}
+      & \textbf{Idris Type} \\
     \hline
@@
 \begin{frame}[fragile]
-  \frametitle{Outline of the problem.}
-  \begin{itemize}
-  \item It's much simpler to prove properties for a small
-        language than a large one.
-  \item We can then design a minimal programming language
-        that is just powerful enough to express our example 
-        protocol, while proving that this language has
-        the properties we desire.
-  \item We could then design a provably correct translation
-        from this language into one more amenable to 
-        production (C, Assembly, etc).
+  \frametitle{Quick Background 3 - Idris Syntax and Functions as Types}
+  Building a vector type in Idris: 
+  \begin{minted}{haskell}
+    data Vec : Nat -> Type -> Type where
+      Nil  : Vec 0 a
+      (::) : (x : a) -> Vec n a -> Vec (n + 1) a
+  \end{minted}
+  We can parameterise types over values to capture invariants in the model.
+  \begin{minted}{haskell}
+    append : Vec n a -> Vec m a -> Vec (n + m) a
+    append Nil ys = ys
+    append (x :: xs) ys = x :: append xs ys 
+  \end{minted}
 \end{frame}
@@
 \begin{frame}[fragile]
-  \frametitle{Prg : A minimal core language}
-  \begin{item} Every expression in this language is paramterised
-          over its supposed running time. 
-  \begin{item} The language can be elaborated into a language nicer
-          to use.
-  \begin{item} The language can also be compiled or translated
-          into a language more amenable for real-life performance.
+  \frametitle{Capturing time invariants in a small DSL}
+  %insert picture for prg here!
 \end{frame}
 
-\begin{frame}[fragile]
-  \frametitle{A diagram of Prg.}
-\end{frame}
-
-\begin{frame}[fragile]
-  \frametitle{Challenges and Outcomes}
-  \begin{itemize}
-    \item Still in the process of confirming whether Prf is 
-            expressive enough for a cryptographic key exchange
-    \item Are there other kinds of proofs we might be interested in
-            on this language to ensure no additional leakage of
-                  information?
-    \item For future work, the implementation of the compilation
-            or translation step in the thorem prover.
-\end{frame}
-
-%\begin{frame}[fragile]
-
-%\end{frame}
-
 \end{document}

### 2019-01-19 Src/talk.tex
some work fleshing out slides, just need to implement diagrams and practice speech

@@
   Applying an argument to a multi argument function returns the 
-  rest of the function! \\ \\
+    rest of the function! (Arrow associates to the right)\\ \\
   $f(2) : \mathbb{N} \rightarrow \mathbb{N}$ \\
@@
 \begin{frame}[fragile]
-  \frametitle{Quick Background 3 - Idris Syntax and Functions as Types}
+  \frametitle{Quick Background 3 - Idris Syntax and Values as Types}
   Building a vector type in Idris: 
@@
   \frametitle{Capturing time invariants in a small DSL}
-  %insert picture for prg here!
+  %code for prg goes here, correct by construction
+  \begin{minted}
+  \end{minted}
 \end{frame}
 
+\begin{frame}[fragile]
+  \frametitle{What about more expressive time parameters?}
+  %discuss how in the case of mod, we can have the time parameter
+  %expressed as a function of the input
+\end{frame}
+
+\begin{frame}[fragile]
+  \frametitle{Elaboration and Compilation of a small correct core}
+  %diagram on how a small correct core can be both elaborated and compiled
+  %for compiled can be mapped to a specific chipset achitecture
+\end{frame}
+
+\begin{frame}[fragile]
+  \frametitle{Contributions}
+  \begin{itemize}
+    \item Formal description of a simplified protocol.
+    \item Prg: A small language parameterised over computational time
+    \item Some small proofs of Prg correctness.
+  \end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+  \frametitle{Further Work}
+  \begin{itemize}
+    \item Implement the simplified protocol in Prg.
+    \item Modulo arithmetic cases.
+    \item Relax some of the (many) assumptions.
+    \item Investigate elaboration and compilation with regard to invariants.
+  \end{itemize}
+\end{frame}
 \end{document}

### 2019-01-20 Src/talk.tex
Finished Talk, need to practice

@@
   \begin{itemize}
-    \item ASD manually verifies vendor code with containing cryptographic
-            processes.
+    \item ASD manually verifies vendor code with containing 
+          cryptographic processes.
     \item Formal Methods: A mathematically based approach to the
@@
     \item Can we reduce some of the resources ASD spends on 
-            manual verification by replacing with automatic verification?
-    \item A case study.
+            manual verification by replacing with automatic 
+            verification?
+    \item A case study, also work towards more secure protocols.
   \end{itemize}
@@
     \item Attackers can gain information from message timing.
-    \item Can we model this invariant? Naively all operations have the
-            same running time.
+    \item Can we model this invariant? Naively all operations 
+          have the same running time.
     \item Can we ensure that assumptions on this model hold for the
@@
     \begin{tabular}{c|c|c|c}
-    \textbf{Logic Term} & \textbf{Logic Symbol} & \textbf{Idris Symbol}
-      & \textbf{Idris Type} \\
+    \textbf{Logic Term} & \textbf{Logic Symbol} & 
+    \textbf{Idris Symbol} & \textbf{Idris Type} \\
     \hline
       Implication & p $\Rightarrow$ q & p \mintinline{haskell}{->} q
-      & Arrow \\
+      & Function \\
       Conjunction & p $\land$ q & \mintinline{haskell}{(p, q)} 
-      & Pair (Product) \\
+      & Pair / Tuple \\
       Disjunction & p $\lor$ q & \mintinline{haskell}{Either p q}
-      & Enum (Sum)\\
+      & Tagged Union\\
       Negation & $\lnot$ p & \mintinline{haskell}{p -> Void} &
       Void Type \\
-      IFF/Eq & p $\equiv$ q, p $\iff$ q & \mintinline{haskell}{(p -> q, q -> p)} 
+      IFF/Eq & p $\equiv$ q, p $\iff$ q & 
+        \mintinline{haskell}{(p -> q, q -> p)} 
       & Pair Arrows \\
@@
   \end{minted}
-  We can parameterise types over values to capture invariants in the model.
+  We can parameterise types over values to capture invariants in 
+  the model.
   \begin{minted}{haskell}
@@
 \begin{frame}[fragile]
-  \frametitle{Capturing time invariants in a small DSL}
-  %code for prg goes here, correct by construction
-  \begin{minted}
+  \frametitle{Building a type of Prg n}
+  \begin{table}[h!]
+  \begin{tabular}{c|c|c|c}
+  Statement & Continuation & Result & Description \\
+  \hline 
+  Halt & Prg 1 & Prg 1 & Terminate \\
+  AssC & Prg k & Prg (k + 1) & Asn constant. \\
+  AssV & Prg k & Prg (k + 1) & Asn variable. \\
+  UnOp & Prg k & Prg (k + 1) & Asn result of unary op. \\
+  BinOP & Prg k & Prg (k + 1) & Asn result of binary op. \\
+  Do & Prg k & Prg (m * n + k) & Run Prg m, n times. \\
+  Cond & Prg k & Prg (n + k) & Branch on Prg n. \\
+  \end{tabular} 
+  \end{table}
+  Conditionals require both branches to be Prg n. Ensuring
+  That all branches of the program are correct by construction.
+\end{frame}
+
+\begin{frame}[fragile]
+  \frametitle{What about more expressive time parameters?}
+  \begin{minted}{haskell}
+  f : Value -> Value -> Nat
+  f = --some complex function to calculate the number of
+      --computation steps for each input to mod.
+
+  data Prg : Nat -> Type where
+    Mod : {k : Nat} -> (cont : Prg k) -> (x : Value) ->
+          (y : Value) -> Prg ((f x y) + k)
   \end{minted}
@@
 \begin{frame}[fragile]
-  \frametitle{What about more expressive time parameters?}
-  %discuss how in the case of mod, we can have the time parameter
-  %expressed as a function of the input
-\end{frame}
+  \frametitle{Elaboration and Compilation of a Correct Core}
+  %diagram on how a small correct core can be both elaborated and 
+  %compiled
+  %for compiled can be mapped to a specific chipset achitecture
+  \begin{minipage}[c]{5cm}
+  \begin{center}
+    \begin{tikzpicture}
+      \node[shape=rectangle, draw=black, minimum size = 2cm] (Elab) 
+           {Elaborator} ;
+      \node[shape=rectangle, draw=black, minimum size = 2cm] (Prg) 
+           [below = 1cm of Elab] {Correct Core};
+      \node[shape=rectangle, draw=black, minimum size = 2cm] (Comp) 
+           [below = 1cm of Prg] {Compiler};
 
-\begin{frame}[fragile]
-  \frametitle{Elaboration and Compilation of a small correct core}
-  %diagram on how a small correct core can be both elaborated and compiled
-  %for compiled can be mapped to a specific chipset achitecture
+      \path [->] (Prg) edge node {} (Elab);
+      \path [->] (Prg) edge node {} (Comp);
+  \end{tikzpicture}
+  \end{center}
+  \end{minipage}
+  \begin{minipage}[c]{\textwidth-6cm}
+  \begin{itemize}
+    \item The small, correct core language can be elaborated to
+          a more full-featured language.
+    \item The size of the core language makes the burden of proofs
+          much lighter.
+    \item The compiler can map the core language expressions down
+          to something more real world (e.g C, assembler).
+  \end{itemize}
+  \end{minipage}
 \end{frame}
@@
     \item Formal description of a simplified protocol.
-    \item Prg: A small language parameterised over computational time
+    \item Prg: A small language parameterised over computational 
+          time
     \item Some small proofs of Prg correctness.
@@
     \item Relax some of the (many) assumptions.
-    \item Investigate elaboration and compilation with regard to invariants.
+    \item Investigate elaboration and compilation with regard to 
+          invariants.
   \end{itemize}

### 2019-01-20 Src/talk.tex
Minor changes
minor changes

@@
     \item Attackers can gain information from message timing.
-    \item Can we model this invariant? Naively all operations 
-          have the same running time.
+    \item Can we model a time-invariant protocol?
+    \item A naive approach considers all operations have the 
+          same running time.
     \item Can we ensure that assumptions on this model hold for the
@@
   All functions treated as taking a single argument. \\ \\
-  $f : \mathbb{N} \rightarrow \mathbb{N} \rightarrow \mathbb{N}$ \\
+  $f : \mathbb{N} \rightarrow (\mathbb{N} \rightarrow \mathbb{N}$) 
+    \\
   $f = + $ \\ \\

### 2019-01-20 Src/talk.tex
more minor changes
some more changes to talk

@@
 
-\title{Verified Time Balancing of Security Protocols}
+\title{Towards Verified Time Balancing of Security Protocols}
 \author{Donovan Crichton}
@@
             verification?
-    \item A case study, also work towards more secure protocols.
+    \item Can we also further research into secure communications
+          protocols?
+    \item A case study.
   \end{itemize}
@@
     \begin{itemize}
-      \item Commit messages contain hashes of 256 bit random nonce.
+      \item Commit messages that contain SHA-256 hashes
       \item Diffie-Hellman key exchange contains modulo arithmetic.
       \item How can we formally guarantee the timing of operations?
+      \item Lets cover some background before diving in!
     \end{itemize}
@@
     \item We can use the notion of propositions as types.
-    \item Dependently typed functional programming languages
-            also act as theorem provers for a higher-order
+    \item Functional programming languages that support dependent
+          types can act as theorem provers under a higher order
           constructive logic.
@@
 \begin{frame}[fragile]
-  \frametitle{Quick Background 2 - Propositions as Types}
+  \frametitle{Quick Background 2 - Idris Syntax and Values as Types}
+  Building a vector type in Idris: 
+  \begin{minted}{haskell}
+    data Vec : Nat -> Type -> Type where
+      Nil  : Vec 0 a
+      (::) : (x : a) -> Vec n a -> Vec (n + 1) a
+  \end{minted}
+  We can parameterise types over values to capture invariants in 
+  the model.
+  \begin{minted}{haskell}
+    append : Vec n a -> Vec m a -> Vec (n + m) a
+    append Nil ys = ys
+    append (x :: xs) ys = x :: append xs ys 
+  \end{minted}
+\end{frame}
+
+\begin{frame}[fragile]
+  \frametitle{Quick Background 3 - Propositions as Types}
+  Under the assumptions of referential transparency and totality.
      \begin{table}[h!]
@@
 \begin{frame}[fragile]
-  \frametitle{Quick Background 3 - Idris Syntax and Values as Types}
-  Building a vector type in Idris: 
-  \begin{minted}{haskell}
-    data Vec : Nat -> Type -> Type where
-      Nil  : Vec 0 a
-      (::) : (x : a) -> Vec n a -> Vec (n + 1) a
-  \end{minted}
-  We can parameterise types over values to capture invariants in 
-  the model.
-  \begin{minted}{haskell}
-    append : Vec n a -> Vec m a -> Vec (n + m) a
-    append Nil ys = ys
-    append (x :: xs) ys = x :: append xs ys 
-  \end{minted}
-\end{frame}
-
-\begin{frame}[fragile]
   \frametitle{Building a type of Prg n}
@@
   \hline 
-  Halt & Prg 1 & Prg 1 & Terminate \\
+  Halt & - & Prg 1 & Terminate \\
   AssC & Prg k & Prg (k + 1) & Asn constant. \\
@@
   Cond & Prg k & Prg (n + k) & Branch on Prg n. \\
+  Skip & Prg k * Prg (k + 1) & Do Nothing.
   \end{tabular} 
@@
     \item The compiler can map the core language expressions down
-          to something more real world (e.g C, assembler).
+          to something more ``real world" (e.g C, assembler).
   \end{itemize}

### 2019-01-20 Src/talk.tex
some more changes to talk

@@
 \begin{frame}[fragile]
+  \frametitle{Correctness by construction}
+  \begin{itemize}
+    \item The protocol implementations can be
+          quite complex, possibly giving rise
+          to equally complex proof obligations.
+    \item We'd like to reduce this burden somehow!
+    \item We can design a language that is just 
+          big enough to compute what we like, 
+          but restrictive enough to capture the
+          invariants we care about.
+  \end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
   \frametitle{Building a type of Prg n}
@@
   Cond & Prg k & Prg (n + k) & Branch on Prg n. \\
-  Skip & Prg k * Prg (k + 1) & Do Nothing.
+  Skip & Prg k & Prg (k + 1) & Do Nothing.
   \end{tabular} 
